[Result, but poetic]: Does LLM Use Improve Data Science Education?

### 2024-08-01 paper/paper.qmd
wrote more paper

library(tidyverse)
library(knitr)
library(kableExtra)
library(lintr)
library(tidyr)

@@

@@

>>>>

library(tidyverse)
library(knitr)
library(kableExtra)
library(lintr)
library(tidyr)
library(quanteda)

@@

TODO: Make a viz of helpfulness in various assignments. Describe the context of the assignment.

```{r fig-AI-helpfulness}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: How Students Use ChatGPT
#| fig-align: center

@@

```{r senti-analysis}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Hello
#| fig-align: center
